Pillar 2 - Topic Modeling

### 2019-03-18 Pillar 2 - Topic Modeling.Rmd
removes repeated code (my_cast_dtm)

## Fitting Model
The function `my_cast_tdm` casts our dataframes into a tdm.
```{r my_cast_tdm, eval = TRUE}
my_cast_tdm <- function(data) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

d_cast <- d_text %>% map(my_cast_tdm)

rm(my_cast_tdm)
```

The function `my_LDA` fits an LDA model on the DTM using the previous controls.
```{r my_LDA, eval= TRUE}

#my_LDA
my_LDA <- function(n_topics, corpus, control = my_control){

@@

Next we train our model with different number of topics.
```{r LDA fit, cache = TRUE, eval = TRUE}
topic_model <- tibble(

@@

##Model Evaluation
###Perplexity
Perplexity is a measure of how well a probability model predicts a sample. Thus we need to do cross validation. 
```{r perplexity function, eval = TRUE}

>>>>

## Fitting Model
The function `my_LDA` fits an LDA model on the DTM using the previous controls.
```{r my_LDA, eval= TRUE}
my_LDA <- function(n_topics, corpus, control = my_control){

@@

We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`
```{r LDA fit, cache = TRUE, eval = TRUE}
topic_model <- tibble(

@@

##Model Evaluation
###Perplexity
Perplexity is a measure of how well a probability model predicts a sample. (Thus may want to do cross validation.) 
```{r perplexity function, eval = TRUE}
